Tourism Data Analysis

### 2019-08-19 Application-R/Application-TourismData/Trash/Results/TourismData-results.Rmd
New results on tourism data

```{r}
AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  as.ts() %>% 
  autoplot()
```

We can see this variable has a very unusual observation which might be an outlier. To avoid this, I have replaced this observation with the average of it's adjacent observations. Then I have refitted the models for automatically chosen BoxCox transformed data and back-transformed and back-transformed bias-adjusted forecasts were obtained. The results are as follows.

@@

DF_BoxCox_2 %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) -> Avg_MSE_BC_2

@@

These results also shows that, even though the bias-adjusted based forecasts are worst than that of biased base forecasts, the MinT reconicilation is outperforming.

```{r}
Avg_MSE_BC_2 %>% filter(`F-method` == "ARIMA_bias", `R-method` == "Base") %>% 
  slice() %>% 
  ungroup() %>% 
  dplyr::select(MSE) %>% 
  as_vector() -> ARIMA_bias_Base

@@

```{r}

@@

DF_MSE %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% 
  spread(key = `R-method`, value = MSE) %>% 
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>% 
  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% 
  gather(`Base-OLS`, `Base-WLS`, `Base-MinT`,  key = Method, value = MSE) %>% 
  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`, scales = "free_y")
```

@@

DF_Log %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) -> Avg_MSE_Log

>>>>

```{r}
AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  ts(start = c(1998, 1), frequency = 12) %>% 
  autoplot()
```

We can see this variable has an anomalous observation on Dec-2002 which might be an outlier.

```{r}
AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  slice(3:102) %>% 
  as.ts() %>% 
  BoxCox.lambda() -> lambda

If we do Box-Cox transformation for this series we get  $\lambda = `r lambda`$. The transformed series with this $\lambda$ looks like

```{r}
AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  slice(3:102) %>% 
  ts(start = c(1998, 1), frequency = 12) %>% 
  BoxCox(lambda = lambda) %>% 
  autoplot()

```{r echo=FALSE}
TS <- AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  slice(3:102) %>% 
  ts(start = c(1998, 1), frequency = 12)
```

```{r echo=FALSE}
# TS %>% 
#   auto.arima(lambda = "auto") %>% 
#   forecast(h=6, biasadj = FALSE) %>% 
#   autoplot() + 
#   ggtitle("Biased forecasts")
# 
# TS %>% 
#   auto.arima(lambda = "auto") %>% 
#   forecast(h=6, biasadj = TRUE) %>% 
#   autoplot() + 
#   ggtitle("Bias-adjusted forecasts")

I have replaced the anomalous observation in this series with the average of December for predecessive and successive years of 2002. Then I have refitted the models for automatically chosen Box-Cox transformed data. Back-transformed and back-transformed bias-adjusted forecasts were then obtained. The results are as follows.

@@

DF_BoxCox_2 %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) -> Avg_MSE_BC_2

@@

These results also shows that, even though the bias-adjusted based forecasts are worst than that of biased base forecasts, the MinT reconciliation is outperforming.

```{r echo=FALSE}
Avg_MSE_BC_2 %>% filter(`F-method` == "ARIMA_bias", `R-method` == "Base") %>% 
  slice() %>% 
  ungroup() %>% 
  dplyr::select(MSE) %>% 
  as_vector() -> ARIMA_bias_Base

@@

```{r echo=FALSE}

@@

DF_MSE %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% 
  spread(key = `R-method`, value = MSE) %>% 
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>% 
  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% 
  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% 
  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% 
  ggplot(aes(x = Method, y = MSE)) + 
  geom_boxplot() + 
  facet_wrap(~`Forecast_Horizon`, scales = "free_y") + 
  ylab("MSE") + xlab("Reconciliation Method")

@@

DF_Log %>% 
  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)/1e3) -> Avg_MSE_Log
